Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-07 Draft/Draft.Rmd
last edits

Indirect interactions (i.e., motifs) commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002] are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation. Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions. However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.

@@

First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies. This was done with the help of hierarchical cluster analysis by using the trait dataset compiled in Lanuza et al., (unpublished). This dataset consisted on x floral, x reproductive and x vegetative traits (Table S2). For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014]. All the numerical traits were previously scaled. Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 [@white2009].

>>>>

Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation. Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions. However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.

@@

First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies. This was done with the help of hierarchical cluster analysis by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species. This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits (Table S2). For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014]. All the numerical traits were previously scaled. Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 [@white2009].
